Hysteresis in human computation:\\ how one task affects another

### 2014-12-04 docs/publications/2014.09_SCIENCE/man.tex
tiny edits

To couch intertask effects in a practical yet general setting, we imagine
that, after a worker performs a task, her response is used to make some 
kind of yes-or-no decision, $\mathcal{D}$.  For example, this decision 
could be whether or not to flag a certain comment
below a news article as inappropriate; but for now, we leave 
$\mathcal{D}$ unspecified.  Since workers' responses may
vary, repeating the same task might lead to different outcomes for 
$\mathcal{D}$.  This decision not only models the reality that responses are
actually used---introducing $\mathcal{D}$ allows us to define \textit{bias}
in a practical yet general way. We shall define bias in terms of the
change in the probability of a positive outcome from $\mathcal{D}$, induced 
by prior exposures.

>>>>

To couch intertask effects in a practical setting, we imagine
that, after a worker performs a task, her response is used to make some 
kind of yes-or-no decision, $\mathcal{D}$.  For example, this decision 
could be whether or not to flag a certain comment
below a news article as inappropriate; but for now, we leave 
$\mathcal{D}$ unspecified.  Since workers' responses may
vary, repeating the same task might lead to different outcomes for 
$\mathcal{D}$.  This decision not only models the reality that responses are
actually used---introducing $\mathcal{D}$ allows us to define \textit{bias}
in a practical yet general way. We define bias in terms of the
change in the probability of a positive outcome from $\mathcal{D}$, induced 
by prior exposures.
